% Decentralized Crypto World Bank — Project Report
% BRAC University — Department of Computer Science and Engineering
% Following BRAC University Thesis/Project Template

\documentclass[11pt,a4paper]{article}

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{mathptmx} % Times New Roman
\usepackage[a4paper,width=150mm,top=25mm,bottom=25mm]{geometry}
\usepackage{setspace}
\singlespacing

\usepackage{amsmath,amssymb}
\usepackage{graphicx}
\usepackage{booktabs}
\usepackage{longtable}
\usepackage{array}
\usepackage{hyperref}
\usepackage{parskip}
\usepackage{fancyhdr}
\usepackage{enumitem}
\usepackage{float}
\usepackage{pmboxdraw}

\hypersetup{
    colorlinks=true,
    linkcolor=black,
    filecolor=magenta,
    urlcolor=black,
    citecolor=black,
}

\begin{document}

%==============================================================================
%  TITLE PAGE
%==============================================================================
\thispagestyle{empty}

\begin{center}

\vspace*{1cm}

{\Large \textbf{Decentralized Crypto World Bank: A Blockchain-Based\\[0.3em] Hierarchical Lending Platform with AI-Enhanced Security}}

\vspace{2.5cm}

by

\vspace{1cm}

Md. Bokhtiar Rahman Juboraz\\
20301138\\[0.8em]
Md. Mahir Ahnaf Ahmed\\
20301083

\vspace{3cm}

A thesis submitted to the Department of Computer Science and Engineering\\
in partial fulfillment of the requirements for the degree of\\
B.Sc. in Computer Science

\vfill

Department of Computer Science and Engineering\\
Brac University\\
February 2026

\vspace{1.5cm}

\copyright\ 2026. Brac University\\
All rights reserved.

\end{center}

\newpage

%==============================================================================
%  DECLARATION PAGE
%==============================================================================
\thispagestyle{empty}

\section*{Declaration}
\addcontentsline{toc}{section}{Declaration}

It is hereby declared that

\begin{enumerate}
\item The thesis submitted is my/our own original work while completing degree at Brac University.

\item The thesis does not contain material previously published or written by a third party, except where this is appropriately cited through full and accurate referencing.

\item The thesis does not contain material which has been accepted, or submitted, for any other degree or diploma at a university or other institution.

\item We have acknowledged all main sources of help.
\end{enumerate}

\vspace{2cm}

\textbf{Student's Full Name \& Signature:}

\vspace{2cm}

\begin{tabular}{p{6cm}p{1cm}p{6cm}}
\hrulefill & & \hrulefill \\
\centering Md. Bokhtiar Rahman Juboraz & & \centering Md. Mahir Ahnaf Ahmed \tabularnewline
\centering 20301138 & & \centering 20301083 \tabularnewline
\end{tabular}

\newpage

%==============================================================================
%  APPROVAL PAGE
%==============================================================================
\thispagestyle{empty}

\section*{Approval}
\addcontentsline{toc}{section}{Approval}

The thesis/project titled ``Decentralized Crypto World Bank: A Blockchain-Based Hierarchical Lending Platform with AI-Enhanced Security'' submitted by

\begin{enumerate}
\item Md. Bokhtiar Rahman Juboraz (20301138)
\item Md. Mahir Ahnaf Ahmed (20301083)
\end{enumerate}

Of Spring, 2026 has been accepted as satisfactory in partial fulfillment of the requirement for the degree of B.Sc. in Computer Science on February 20, 2026.

\vspace{1cm}

\textbf{Examining Committee:}

\vspace{1.5cm}

\begin{flushleft}
Supervisor:\\
(Member)
\end{flushleft}

\begin{flushright}
\vspace{-0.5cm}
\hrulefill\\
Mr. Annajiat Alim Rasel\\
Senior Lecturer\\
Department of Computer Science and Engineering\\
Brac University
\end{flushright}

\vspace{1.5cm}

\begin{flushleft}
Thesis Coordinator:\\
(Member)
\end{flushleft}

\begin{flushright}
\vspace{-0.5cm}
\hrulefill\\
\mbox{[Thesis Coordinator Name]}\\
\mbox{[Designation]}\\
Department of Computer Science and Engineering\\
Brac University
\end{flushright}

\vspace{1.5cm}

\begin{flushleft}
Head of Department:\\
(Chair)
\end{flushleft}

\begin{flushright}
\vspace{-0.5cm}
\hrulefill\\
Dr. Sadia Hamid Kazi\\
Chairperson and Associate Professor\\
Department of Computer Science and Engineering\\
Brac University
\end{flushright}

\newpage

%==============================================================================
%  ABSTRACT PAGE
%==============================================================================

\begin{abstract}
\addcontentsline{toc}{section}{Abstract}

International development finance relies on multi-tiered institutional hierarchies---from supranational reserves to national intermediaries to local disbursement entities---to coordinate the flow of capital across borders. These conventional systems, while providing governance and risk management, suffer from limited transparency, protracted settlement cycles, and opaque decision-making processes that erode stakeholder trust.

This project presents the \textbf{Crypto World Bank}, a decentralized application (DApp) that replicates the hierarchical lending model of traditional development finance institutions on a public Ethereum Virtual Machine (EVM) blockchain. The platform enforces a four-tier capital flow (World Bank $\to$ National Banks $\to$ Local Banks $\to$ Borrowers) through a suite of auditable smart contracts, while augmenting loan approval workflows with an off-chain AI/ML security layer for fraud detection, anomaly identification, and explainable risk assessment.

We demonstrate that blockchain technology is uniquely suited to this domain because the underlying challenge is fundamentally one of \textbf{multi-party trust and coordination}---a class of problems for which distributed ledger technology provides superior guarantees over conventional centralized architectures. The document further presents the target market, partnership ecosystem, competitive landscape, risk profile, system architecture, governance framework, and a phased go-to-market strategy.

\vspace{0.5em}
\noindent\textbf{Keywords:} Blockchain, Decentralized Finance, Hierarchical Lending, Smart Contracts, AI/ML Security, Fraud Detection, Explainable AI, Governance, Development Finance
\end{abstract}

\newpage
\setcounter{page}{1}
\tableofcontents
\newpage

%==============================================================================
\section{Literature Review}
%==============================================================================

The design of the Crypto World Bank is informed by a comprehensive review of 17 peer-reviewed papers spanning seven domains. Full detailed reviews (Abstract, Introduction, Motivation, Methodology, Results, Conclusion) for all papers are available in the project documentation repository.

\textbf{Decentralized Lending and DeFi Protocols.} Werner et al.~[10] systematize DeFi protocol design in their SoK paper, identifying that existing lending platforms are uniformly pool-based and over-collateralized, lacking institutional hierarchy—a gap this project directly addresses. Bastankhah et al.~[1] introduce an adaptive, data-driven DeFi lending protocol with a dual fast/slow control architecture, demonstrating that dynamic interest rate adjustment significantly outperforms static utilization curves used by Aave and Compound. An IEEE evaluation framework [9] provides standardized metrics for assessing protocol capital efficiency, risk management, and governance quality, revealing that higher capital efficiency correlates with higher risk exposure.

\textbf{ML Fraud Detection in Blockchain.} Palaiokrassas et al.~[2] leverage ML for multichain DeFi fraud detection across 23 protocols (54M+ transactions), demonstrating that DeFi-specific behavioral features improve XGBoost and Neural Network classifiers to F1-scores of 0.76--0.85, compared to 0.08 with transactional features alone. Agarwal et al.~[3] present RiskSEA, a scalable graph embedding system deployed at Coinbase that combines node2vec embeddings with behavioral features, achieving F1: 0.851 on all 266M Ethereum addresses. Rahouti et al.~[16] survey ML approaches for Bitcoin security, finding Random Forest achieves 94\%+ precision—supporting its selection as the primary fraud detection model in this system.

\textbf{Explainable AI in Lending.} Adom et al.~[4] provide a direct comparison of LIME and SHAP on loan approval systems, finding SHAP provides deeper, more consistent feature attributions via Shapley values, while LIME offers faster runtime. Lundberg and Lee [11] introduce the SHAP framework itself, providing the theoretical foundation (local accuracy, missingness, consistency properties) that this system adopts for generating explainable loan risk assessments. Bracke et al.~[17] apply SHAP to credit default models in a Bank of England regulatory context, demonstrating that SHAP feature attributions align with domain expert expectations and satisfy regulatory explainability requirements.

\textbf{Reinforcement Learning for Lending Policy.} Qu et al.~[5] apply offline RL (CQL, BC, TD3-BC) to optimize Aave interest rates using historical data, with TD3-BC demonstrating superior performance during stress events (May 2021 crash, March 2023 USDC depeg). Kiatsupaibul et al.~[6] formulate credit underwriting as an MDP, showing RL-based approaches discover superior underwriting policies compared to traditional greedy (static threshold) methods—validating our planned DQN/PPO modules for adaptive borrowing limits.

\textbf{CBDC and Financial Inclusion.} Tan [7] develops an IMF model showing CBDCs in developing countries can bank large unbanked populations through a two-tier distribution model (central bank $\to$ commercial banks $\to$ users) that directly parallels our four-tier hierarchy. Mhlanga [8] demonstrates through systematic review that blockchain technology facilitates financial inclusion across transactions, savings, credit provision, and insurance—supporting the Crypto World Bank's mission of transparent, programmable lending for underserved populations.

\textbf{Smart Contract Security and Governance.} Atzei et al.~[13] catalog Ethereum smart contract attack vectors (reentrancy, integer overflow, access control), directly informing our use of OpenZeppelin's ReentrancyGuard and Solidity 0.8.20 overflow protection. Tolmach et al.~[15] survey 42 formal verification tools, recommending multi-tool approaches combining static analysis (Slither) and symbolic execution (Mythril). Beck et al.~[14] propose a three-dimensional blockchain governance framework (IT, network, business) that maps directly to our three-pillar governance structure. Liu et al.~[12] introduce Isolation Forest for unsupervised anomaly detection—adopted as our secondary detection model for wallet behavior analysis where labeled fraud data is scarce.

\textbf{Identified Gaps.} Across these 17 papers, four gaps motivate the Crypto World Bank: (1) no hierarchical institutional model exists in DeFi lending [10, 1, 9]; (2) limited integration of AI/ML security analytics with DeFi lending [2, 3, 16]; (3) insufficient explainability in automated lending decisions [4, 11, 17]; and (4) inadequate governance frameworks for multi-tier decentralized finance systems [14].

%==============================================================================
\section{Problem Statement and Proposed Solution}
%==============================================================================

\subsection{Problem Formulation}

The global development finance ecosystem is characterized by a hierarchical topology in which supranational entities (e.g., the World Bank, International Monetary Fund) allocate capital to sovereign national institutions, which in turn disburse funds to regional and local banking entities, ultimately reaching end-user borrowers. This multi-layered intermediation introduces several systemic inefficiencies:

\begin{enumerate}[noitemsep]
\item \textbf{Opacity of ledger state.} Internal bookkeeping across tiers is not publicly auditable. Stakeholders at lower tiers have limited visibility into reserve adequacy, approval criteria, and fund utilization at higher tiers.

\item \textbf{Settlement latency.} Cross-border capital transfers between tiers involve multiple intermediaries, compliance checkpoints, and reconciliation processes, resulting in settlement periods ranging from days to weeks.

\item \textbf{Manual risk assessment.} Creditworthiness evaluation and fraud detection are predominantly human-driven, introducing inconsistency, bias, and scalability constraints.

\item \textbf{Trust deficit.} The effort required to establish inter-institutional trust through legal agreements, audit engagements, and compliance certifications constitutes a significant overhead that disproportionately affects smaller institutions and borrowers in developing economies.
\end{enumerate}

Simultaneously, the Decentralized Finance (DeFi) ecosystem has demonstrated that smart contract platforms can automate lending, collateral management, and interest computation with full transparency. However, existing DeFi protocols (e.g., Aave, Compound, MakerDAO) exhibit fundamental limitations in this context:

\begin{itemize}[noitemsep]
\item They employ \textbf{peer-to-pool} or \textbf{over-collateralized} lending models that do not accommodate institutional hierarchies.
\item They lack integration with \textbf{AI-driven risk analytics} and \textbf{explainable decision support} systems.
\item They do not model \textbf{role-based, tiered governance} analogous to development finance institutions.
\end{itemize}

\subsection{Blockchain Justification}

The problem described above is fundamentally a \textbf{multi-party coordination and trust challenge} involving disparate institutions with potentially misaligned incentives. We assert that blockchain technology addresses this class of problems more effectively than any conventional alternative for the following reasons:

\begin{enumerate}[noitemsep]
\item \textbf{Trust minimization through consensus.} Distributed consensus mechanisms ensure that no single party can unilaterally alter the ledger state, eliminating the need for a trusted central operator.

\item \textbf{Programmable enforcement.} Smart contracts codify lending rules—borrowing limits, installment schedules, approval workflows—as deterministic, self-executing programs, reducing reliance on manual processes and bilateral agreements.

\item \textbf{Cryptographic auditability.} All state transitions are recorded in an immutable, publicly verifiable transaction log, enabling real-time auditing by regulators, partners, and borrowers without requiring costly third-party engagements.

\item \textbf{Composable incentive structures.} On-chain reputation systems, governance tokens, and programmable fee distributions can align incentives across all network participants.
\end{enumerate}

A conventional cloud-hosted database infrastructure would necessitate a trusted central operator to maintain ledger integrity, enforce access control, and provide audit guarantees—reintroducing the very trust dependencies that the hierarchical lending model seeks to mitigate. Blockchain eliminates this single point of trust failure.

\subsection{Proposed Solution}

The Crypto World Bank implements a \textbf{four-tier, on-chain hierarchical lending architecture}:

\begin{itemize}[noitemsep]
\item \textbf{Tier 1 — World Bank:} Maintains the global crypto reserve. Allocates capital to registered National Banks through smart contract-mediated lending operations.
\item \textbf{Tier 2 — National Banks:} Borrow from the World Bank reserve. Lend to registered Local Banks within their jurisdiction. Aggregate risk exposure at the national level.
\item \textbf{Tier 3 — Local Banks:} Borrow from National Banks. Process loan requests from individual borrowers. Employ designated approvers for loan lifecycle management.
\item \textbf{Tier 4 — Borrowers:} Submit loan requests to Local Banks. Repay through configurable installment schedules. Accumulate on-chain repayment history that informs future borrowing limits.
\end{itemize}

The platform further integrates:

\begin{itemize}[noitemsep]
\item \textbf{Risk-aware borrowing limits} computed from rolling 6-month and 1-year transaction windows.
\item \textbf{Automatic installment generation} for loan amounts exceeding a configurable threshold (e.g., 100 ETH equivalent).
\item \textbf{Off-chain AI/ML security analytics} for fraud detection (Random Forest), anomaly identification (Isolation Forest), and explainable risk assessment (SHAP).
\end{itemize}

%==============================================================================
\section{Market Analysis and Partnership Ecosystem}
%==============================================================================

\subsection{Market Sizing}

\begin{table}[H]
\centering
\caption{Market segments.}
\begin{tabular}{|l|l|l|}
\hline
\textbf{Segment} & \textbf{Description} & \textbf{Estimated Scale} \\
\hline
Total Addressable Market (TAM) & Global decentralized lending market; DeFi lending TVL has historically exceeded \$50B & \$50B+ \\
\hline
Serviceable Addressable Market (SAM) & Institutional and semi-institutional lending requiring hierarchical structures & \$5--10B \\
\hline
Serviceable Obtainable Market (SOM) & Pilot deployments in regulatory sandboxes, academic prototypes, NGO-backed microfinance & \$50--200M \\
\hline
\end{tabular}
\end{table}

The market for \textbf{transparent, hierarchy-preserving decentralized lending} is presently unaddressed by existing DeFi protocols, which universally adopt flat, pool-based architectures. This represents a significant whitespace opportunity.

\subsection{Target Customer Segment}

The Crypto World Bank targets the \textbf{retail customer segment} --- individual borrowers and small businesses seeking transparent, accessible crypto-based lending services.

\begin{table}[H]
\centering
\caption{Target customer segment profile.}
\small
\begin{tabular}{|p{3.5cm}|p{8cm}|}
\hline
\textbf{Characteristic} & \textbf{Description} \\
\hline
Primary Users & Individual retail borrowers seeking personal or small business loans \\
\hline
Geographic Focus & Developing economies with limited traditional banking access (e.g., Bangladesh, Southeast Asia, Sub-Saharan Africa) \\
\hline
Loan Size Range & Micro to mid-range: 0.1 ETH -- 500 ETH equivalent (\textasciitilde\$200 -- \$1,000,000 at current rates) \\
\hline
User Profile & Digitally literate individuals with cryptocurrency wallet access; small business owners; gig-economy freelancers \\
\hline
Key Pain Points & High interest rates from informal lenders; lack of credit history in traditional systems; exclusion from banking due to documentation barriers \\
\hline
\end{tabular}
\end{table}

\textbf{Why Retail:} The retail segment represents the largest underserved population in developing economies. According to the World Bank's Global Findex Database, approximately 1.4 billion adults remain unbanked, with the majority concentrated in developing countries. By targeting retail customers, the platform maximizes financial inclusion impact while generating the transaction volume necessary to sustain the lending ecosystem. The hierarchical banking model (World Bank $\to$ National $\to$ Local $\to$ Borrower) mirrors how traditional microfinance institutions reach retail customers in underserved regions, but with blockchain-enforced transparency and AI-enhanced risk assessment.

\subsection{Partner Ecosystem}

\begin{table}[H]
\centering
\caption{Partner categories and roles.}
\small
\begin{tabular}{|p{3.2cm}|p{4cm}|p{4.5cm}|}
\hline
\textbf{Partner Category} & \textbf{Functional Role} & \textbf{Blockchain-Mediated Incentive} \\
\hline
Financial Regulators & Regulatory sandbox approval; compliance oversight & Reduced enforcement cost through on-chain transparency and audit trails \\
\hline
Banking Institutions & Network membership as National/Local Banks & Access to diversified global reserve; reduced inter-bank settlement friction \\
\hline
Payment Gateway Providers & Fiat-to-crypto on-ramp and off-ramp services & Volume-based transaction fees; expanded market reach \\
\hline
Academic and Research Institutions & Validation of AI/ML models; publication of research findings & Access to anonymized datasets; collaborative research opportunities \\
\hline
Non-Governmental Organizations & Pilot deployment; field testing with underserved borrower populations & Transparent, low-friction credit access for beneficiaries \\
\hline
\end{tabular}
\end{table}

\subsection{Incentive Alignment Through the Blockchain Platform}

Partner incentives are allocated and enforced through the blockchain platform itself:

\begin{itemize}[noitemsep]
\item \textbf{Immutable repayment records} serve as on-chain reputation signals, enabling data-driven credit decisions without third-party credit bureaus.
\item \textbf{Transparent reserve verification} allows partners to independently confirm that allocated capital is deployed as committed.
\item \textbf{Programmable fee structures} (future extension) distribute transaction fees proportionally to network participants based on their contribution to lending volume and governance.
\end{itemize}

%==============================================================================
\section{Competitive Landscape and Risk Assessment}
%==============================================================================

\subsection{Direct Competition}

\begin{table}[H]
\centering
\caption{Direct competition.}
\small
\begin{tabular}{|p{2.5cm}|p{3.2cm}|p{5cm}|}
\hline
\textbf{Competitor Category} & \textbf{Representative Examples} & \textbf{Crypto World Bank Differentiation} \\
\hline
DeFi lending protocols & Aave, Compound, MakerDAO & Hierarchical four-tier institutional model; integrated AI/ML risk layer; role-based governance \\
\hline
Traditional development finance & World Bank, IFC, ADB & On-chain transparency; programmable enforcement; near-instant settlement \\
\hline
Blockchain-native credit platforms & Centrifuge, Maple Finance, Goldfinch & Combined hierarchy and AI security; designed for institutional adoption \\
\hline
\end{tabular}
\end{table}

\subsection{Indirect Competition}

\begin{itemize}[noitemsep]
\item \textbf{Central Bank Digital Currencies (CBDCs):} Emerging CBDC frameworks may address settlement efficiency but do not provide decentralized lending capabilities. The Crypto World Bank positions as a complementary \textbf{lending layer} operating on top of digital asset infrastructure.
\item \textbf{Peer-to-peer lending platforms:} Predominantly fiat-denominated and centralized; the Crypto World Bank targets crypto-native and hybrid institutional use cases.
\end{itemize}

\subsection{Risk Taxonomy and Mitigation Strategy}

\begin{table}[H]
\centering
\caption{Risk taxonomy and mitigation.}
\small
\begin{tabular}{|p{2.2cm}|p{3.2cm}|c|p{3.8cm}|}
\hline
\textbf{Risk Category} & \textbf{Description} & \textbf{Sev.} & \textbf{Mitigation} \\
\hline
Partner non-cooperation & Key ecosystem partners decline to participate & M & Initiate with low-barrier academic and NGO pilots; minimize switching costs \\
\hline
Incentive misalignment & Participant incentives diverge from network objectives & M & Codify rules in smart contracts; implement governance token alignment (future) \\
\hline
Smart contract vulnerability & Exploit in contract logic (reentrancy, overflow) & H & OpenZeppelin security primitives; formal audit (planned); pause mechanism \\
\hline
Regulatory adversity & Jurisdictional restrictions on crypto lending & M & Operate exclusively on testnets during prototype phase; engage regulatory sandbox programs \\
\hline
Market adoption failure & Insufficient user or institutional traction & L & Leverage academic and competition channels; open-source codebase \\
\hline
AI/ML model degradation & Fraud detection accuracy decays over time & L & Continuous model retraining pipeline; human-in-the-loop review; explainability via SHAP \\
\hline
\end{tabular}
\end{table}

\subsection{Comparative Advantage}

\begin{itemize}[noitemsep]
\item \textbf{Value delivery superiority:} Blockchain-enforced transparency eliminates reconciliation overhead; AI/ML augments human judgment with data-driven risk scores.
\item \textbf{Performance superiority:} Sub-minute transaction confirmation on EVM Layer-2 networks (Polygon) versus multi-day settlement in traditional development finance.
\end{itemize}

%==============================================================================
\section{System Architecture and Governance Framework}
%==============================================================================

\subsection{High-Level Architecture}

The system employs a \textbf{three-layer decentralized application architecture}:

\begin{center}
\setlength{\fboxsep}{10pt}
\setlength{\fboxrule}{0.6pt}

\fbox{\parbox{0.88\textwidth}{%
\textbf{PRESENTATION LAYER}\\[3pt]
React 18 \(\cdot\) TypeScript \(\cdot\) Material Design 3 \(\cdot\) Wagmi \(\cdot\) Viem\\[2pt]
Modules: Dashboard, Deposit, Loan, Admin, Risk AI, QR%
}}

\vspace{6pt}
{\Large $\downarrow$}
\vspace{6pt}

\fbox{\parbox{0.88\textwidth}{%
\textbf{SMART CONTRACT LAYER (EVM: Ethereum / Polygon)}\\[3pt]
World Bank Reserve Contract \(\cdot\) National Bank Contract \(\cdot\) Local Bank Contract\\[2pt]
Operations: Reserve Mgmt, Hierarchical Lending, Loan Lifecycle,\\
Access Control, Emergency Controls%
}}

\vspace{6pt}
{\Large $\downarrow$}
\vspace{6pt}

\fbox{\parbox{0.88\textwidth}{%
\textbf{OFF-CHAIN SERVICES LAYER}\\[3pt]
PostgreSQL (Relational DB) \(\cdot\) FastAPI (REST API)\\[2pt]
AI/ML: Random Forest (Fraud) \(\cdot\) Isolation Forest (Anomaly)\\[2pt]
SHAP (Explainability) \(\cdot\) Event Listener \(\cdot\) Cache (Redis)%
}}
\end{center}

\subsection{Blockchain Platform Selection}

\begin{table}[H]
\centering
\caption{Blockchain platform selection.}
\begin{tabular}{|l|l|l|}
\hline
\textbf{Criterion} & \textbf{Selection} & \textbf{Justification} \\
\hline
Platform & Ethereum Virtual Machine (EVM) & Largest developer ecosystem; battle-tested security model; extensive tooling \\
\hline
Network & Polygon Mumbai / Ethereum Sepolia (testnets) & Zero-cost deployment; production-equivalent behavior; free faucet access \\
\hline
Consensus & Proof-of-Stake (PoS) via Polygon validators & Energy-efficient; sub-2-second block finality; decentralized validator set \\
\hline
Smart contract language & Solidity 0.8.20 & Industry standard; mature compiler with overflow protection; rich library ecosystem \\
\hline
\end{tabular}
\end{table}

\subsection{Transaction Verification and Consensus}

\begin{itemize}[noitemsep]
\item \textbf{Polygon PoS:} Transactions are validated by a decentralized set of PoS validators. Block finality is achieved within approximately 2 seconds. Checkpoints are periodically committed to Ethereum mainnet for additional security.
\item \textbf{On prototype testnets:} Mumbai and Sepolia employ analogous consensus models with no financial cost, enabling iterative development and testing.
\end{itemize}

\subsection{On-Chain and Off-Chain Data Partitioning}

\begin{table}[H]
\centering
\caption{Data partitioning.}
\small
\begin{tabular}{|p{4.2cm}|p{2.5cm}|p{5cm}|}
\hline
\textbf{Data Category} & \textbf{Storage} & \textbf{Rationale} \\
\hline
Reserve balances, loan requests, approval/rejection events, repayment transactions & On-chain & Immutability, public auditability, trustless verification \\
\hline
User profiles, income verification documents, chat messages, AI/ML inference logs & Off-chain (PostgreSQL) & Data privacy, query flexibility, storage cost optimization \\
\hline
Borrowing limit computations & Off-chain with on-chain enforcement & Complex temporal aggregation; results committed as on-chain constraints \\
\hline
Cryptocurrency market data & Off-chain (cached) & High-frequency updates; external API dependency \\
\hline
\end{tabular}
\end{table}

\subsection{Data Model}

The relational database schema comprises 15 normalized entities in Third Normal Form (3NF):

\textbf{Core hierarchy:} \texttt{WORLD\_BANK}, \texttt{NATIONAL\_BANK}, \texttt{LOCAL\_BANK}, \texttt{BANK\_USER}, \texttt{BORROWER}

\textbf{Lending lifecycle:} \texttt{LOAN\_REQUEST}, \texttt{INSTALLMENT}, \texttt{TRANSACTION}, \texttt{BORROWING\_LIMIT}

\textbf{Communication:} \texttt{CHAT\_MESSAGE}

\textbf{AI/ML and security:} \texttt{AI\_CHATBOT\_LOG}, \texttt{AI\_ML\_SECURITY\_LOG}

\textbf{Supporting:} \texttt{INCOME\_PROOF}, \texttt{MARKET\_DATA}, \texttt{PROFILE\_SETTINGS}

A comprehensive Entity-Relationship Diagram (ERD) is maintained in the project documentation repository.

\subsection{Digital Identity System}

\begin{itemize}[noitemsep]
\item \textbf{Wallet-based identity:} Users authenticate via Ethereum wallet signatures (MetaMask, WalletConnect). No centralized credential store is required.
\item \textbf{Role binding:} Wallet addresses are mapped to hierarchical roles (Owner, National Bank, Local Bank, Approver, Borrower) within the smart contract permission system.
\end{itemize}

\subsection{Integration with Legacy Systems}

\begin{itemize}[noitemsep]
\item \textbf{Current:} Standard Web3 wallet integration (MetaMask browser extension, WalletConnect mobile protocol).
\item \textbf{Planned:} Fiat on-ramp/off-ramp via payment gateway APIs; KYC/AML compliance via external identity verification providers.
\end{itemize}

\subsection{Auxiliary Dual-Currency Facility}

The Crypto World Bank's cryptocurrency exchange capability is designed as an \textbf{auxiliary facility} integrated into existing banking infrastructure worldwide. Rather than operating as a standalone exchange, the platform extends the services of participating banks by enabling a \textbf{dual-currency feature}---allowing eligible bank customers to transact in both fiat and cryptocurrency within their existing banking relationship.

\begin{itemize}[noitemsep]
\item \textbf{Integration model:} The dual-currency facility is offered by all participating banks (World Bank, National Banks, and Local Banks) as an add-on service to their existing product portfolio. No new banking license or standalone entity is required.
\item \textbf{Eligibility determination:} Eligibility for dual-currency services is determined by the bank officers who manage lending operations. These officers assess customer suitability based on existing KYC/AML compliance, account standing, and lending relationship history.
\item \textbf{No defaulting of conditions:} The project does not override, modify, or default any existing banking conditions, regulatory requirements, or contractual obligations. All existing banking terms, interest rate agreements, and compliance frameworks remain fully in effect.
\item \textbf{Scope:} The facility enables fiat-to-crypto and crypto-to-fiat conversions, cryptocurrency-denominated lending and repayment, and transparent on-chain transaction records---all within the governance structure of the participating bank.
\end{itemize}

This design ensures that the Crypto World Bank \textbf{complements rather than disrupts} existing financial infrastructure, reducing adoption barriers for traditional banking institutions and their customers.

\subsection{Regulatory Compliance Considerations}

As the platform operates within the regulated banking domain:
\begin{itemize}[noitemsep]
\item The prototype phase operates exclusively on \textbf{public testnets} with no real monetary value.
\item The architecture supports \textbf{audit log generation} for regulatory review.
\item Future production deployment would engage \textbf{regulatory sandbox programs} in target jurisdictions.
\end{itemize}

\subsection{Governance Framework}

\subsubsection{Network Membership Governance}

\begin{table}[H]
\centering
\small
\begin{tabular}{|p{3.5cm}|p{8cm}|}
\hline
\textbf{Governance Aspect} & \textbf{Implementation} \\
\hline
Member on-boarding & World Bank owner registers National Banks; National Banks register Local Banks; Local Banks designate approvers --- all enforced on-chain \\
\hline
Member off-boarding & Deactivation flags in smart contracts; cascading access revocation \\
\hline
Regulatory oversight & Audit log emission via smart contract events; planned read-only regulator dashboard \\
\hline
Permission structure & Hierarchical: Owner $\to$ National Bank $\to$ Local Bank $\to$ Approver $\to$ Borrower; enforced by on-chain role-check modifiers \\
\hline
Network operations & Pause/unpause mechanism for emergency response; emergency withdrawal for critical situations \\
\hline
\end{tabular}
\end{table}

\subsubsection{Business Network Governance}

\begin{table}[H]
\centering
\small
\begin{tabular}{|p{3.5cm}|p{8cm}|}
\hline
\textbf{Governance Aspect} & \textbf{Implementation} \\
\hline
Business charter & Defined in this whitepaper; operational parameters codified in smart contract constants \\
\hline
Common services & Reserve management, loan lifecycle orchestration, event-driven notification system \\
\hline
Business SLA & Testnet phase: best-effort availability. Production phase: 99.5\% target uptime with multi-region deployment \\
\hline
Regulatory compliance & Architecture designed for audit trail generation; data partitioning supports GDPR-style data subject requests \\
\hline
\end{tabular}
\end{table}

\subsubsection{Technology Infrastructure Governance}

\begin{table}[H]
\centering
\small
\begin{tabular}{|p{3.5cm}|p{8cm}|}
\hline
\textbf{Governance Aspect} & \textbf{Implementation} \\
\hline
Distributed IT structure & Client-side frontend (decentralized delivery); blockchain layer (fully decentralized); backend API (centralized, horizontally scalable) \\
\hline
Technology assessment & Continuous evaluation of EVM alternatives (L2 rollups, sidechains) for cost and performance optimization \\
\hline
On-chain / off-chain data services & Clearly partitioned (see Section IV.D); event listeners synchronize state between layers \\
\hline
Risk mitigation & Smart contract pause mechanism; ReentrancyGuard; input validation; planned formal security audit \\
\hline
\end{tabular}
\end{table}

\subsection{Asset Tokenization}

\begin{itemize}[noitemsep]
\item \textbf{Current implementation:} Native blockchain currency (ETH/MATIC) serves as the reserve and loan denomination.
\item \textbf{Planned extension:} ERC-20 stablecoin support (USDC, USDT) for USD-denominated lending operations; tokenized collateral instruments for under-collateralized lending scenarios.
\end{itemize}

\subsection{Transaction Economics: Gas Fees and Interest Rates}

\subsubsection{Gas Fee Policy}

All blockchain transaction costs (gas fees) are borne by the \textbf{transaction initiator}, following standard Ethereum/Polygon network conventions:

\begin{table}[H]
\centering
\caption{Gas fee responsibility by transaction type.}
\small
\begin{tabular}{|p{3.8cm}|p{3cm}|p{4.5cm}|}
\hline
\textbf{Transaction Type} & \textbf{Gas Fee Payer} & \textbf{Rationale} \\
\hline
Loan Request & Borrower & Borrower initiates the loan request transaction \\
\hline
Loan Approval & Bank Approver & Approver initiates the approval transaction \\
\hline
Loan Rejection & Bank Approver & Approver initiates the rejection transaction \\
\hline
Installment Payment & Borrower & Borrower initiates each installment payment \\
\hline
Deposit to Reserve & Depositor & Depositor initiates the reserve contribution \\
\hline
Bank Registration & Registering Authority & World Bank Admin or National Bank initiates registration \\
\hline
\end{tabular}
\end{table}

On \textbf{Polygon PoS} (the primary target network), gas fees are denominated in MATIC and are significantly lower than Ethereum mainnet --- typically \textbf{\$0.001--\$0.01 per transaction}, making the platform economically viable for retail users with smaller loan amounts. This low fee structure is critical for the retail customer segment, where even small transaction costs can disproportionately affect borrower economics.

\subsubsection{Interest Rate Structure}

The platform implements \textbf{market-standard interest rates} aligned with prevailing DeFi lending benchmarks:

\begin{table}[H]
\centering
\caption{Interest rate parameters.}
\small
\begin{tabular}{|p{3.5cm}|p{3.5cm}|p{4.5cm}|}
\hline
\textbf{Parameter} & \textbf{Value} & \textbf{Benchmark} \\
\hline
Base Annual Interest Rate & 5--12\% APR & Aligned with Aave/Compound variable rates for major crypto assets \\
\hline
Rate Determination & Set by Local Bank approvers within World Bank-defined bounds & Configurable per-bank to reflect local market conditions \\
\hline
Late Payment Penalty & 2\% of installment amount + 0.5\% per additional week overdue (capped at 10\%) & Industry-standard late fee structure \\
\hline
Interest Calculation & Simple interest on outstanding principal & Transparent, borrower-friendly method \\
\hline
Rate Transparency & All rate parameters stored on-chain as smart contract constants & Publicly auditable; no hidden fees \\
\hline
\end{tabular}
\end{table}

Interest rates are designed to balance lending sustainability with borrower affordability. The on-chain storage of rate parameters ensures borrowers can independently verify loan terms before execution. Local Banks may adjust rates within the bounds set by the World Bank tier, allowing localized pricing that reflects regional economic conditions.

%==============================================================================
\section{Methodology}
%==============================================================================

\subsection{Development Methodology}

The project adopts a \textbf{lightweight Agile/Scrum} methodology tailored for an academic prototype with a fixed two-month development window. The iterative approach enables incremental delivery of demonstrable features while accommodating evolving requirements inherent in research-oriented development.

\begin{center}
\setlength{\fboxsep}{8pt}
\setlength{\fboxrule}{0.6pt}

\fbox{\parbox{0.92\textwidth}{%
\centering\textbf{AGILE DEVELOPMENT LIFECYCLE} --- 2-Month Window%
}}

\vspace{12pt}

\fbox{\begin{minipage}[t]{0.27\textwidth}
\centering\textbf{SPRINT 1}\\(Weeks 1--3)\\[6pt]
\raggedright\textbf{Foundation \&\\Core Banking}\\[4pt]
{\small%
\begin{itemize}[noitemsep,leftmargin=*,topsep=0pt]
\item Smart contract development
\item Frontend setup
\item Wallet integration
\item Dashboard \& Deposit flow
\item Database schema
\end{itemize}}
\end{minipage}}%
\hfill{\Large $\Rightarrow$}\hfill%
\fbox{\begin{minipage}[t]{0.27\textwidth}
\centering\textbf{SPRINT 2}\\(Weeks 4--6)\\[6pt]
\raggedright\textbf{Lending Features\\  \& Communication}\\[4pt]
{\small%
\begin{itemize}[noitemsep,leftmargin=*,topsep=0pt]
\item Installment payment system
\item Borrowing limit enforcement
\item Chat system
\item Income verification
\item Bank hierarchy
\end{itemize}}
\end{minipage}}%
\hfill{\Large $\Rightarrow$}\hfill%
\fbox{\begin{minipage}[t]{0.27\textwidth}
\centering\textbf{SPRINT 3}\\(Weeks 7--8)\\[6pt]
\raggedright\textbf{AI/ML Security\\  \& Polish}\\[4pt]
{\small%
\begin{itemize}[noitemsep,leftmargin=*,topsep=0pt]
\item Fraud detection model
\item Risk dashboard integration
\item Security audit
\item Documentation
\item Demo prep
\end{itemize}}
\end{minipage}}
\end{center}

\subsection{Agile Sprint Plan (8-Week Schedule)}

\begin{table}[H]
\centering
\caption{Sprint plan.}
\small
\begin{tabular}{|p{1.2cm}|p{1.5cm}|p{2.2cm}|p{6.5cm}|}
\hline
\textbf{Sprint} & \textbf{Duration} & \textbf{Goal} & \textbf{Key Deliverables} \\
\hline
Sprint 1 & Weeks 1--3 & Foundation and Core Banking & Smart contract suite (WorldBankReserve, NationalBank, LocalBank); React frontend scaffolding; wallet integration; Dashboard and Deposit pages; database schema (15 tables, 3NF) \\
\hline
Sprint 2 & Weeks 4--6 & Lending Features and Communication & Loan request and approval workflow; installment payment system; borrowing limit engine; borrower--bank chat; income verification; hierarchical bank registration \\
\hline
Sprint 3 & Weeks 7--8 & AI/ML Security and Finalization & Fraud detection model (Random Forest + SHAP); risk dashboard; anomaly detection prototype; security audit; documentation; demo preparation \\
\hline
\end{tabular}
\end{table}

\subsection{User Stories per Sprint}

\textbf{Sprint 1 — Foundation}
\begin{itemize}[noitemsep]
\item US-1.1: As a user, I want to connect my wallet so that I can interact with the platform.
\item US-1.2: As a user, I want to deposit to the reserve so that the bank has funds to lend.
\item US-1.3: As an admin, I want to register National Banks so that the hierarchy is established.
\item US-1.4: As a developer, I want a normalized database schema so that all entities are properly modeled.
\end{itemize}

\textbf{Sprint 2 — Lending}
\begin{itemize}[noitemsep]
\item US-2.1: As a borrower, I want to request a loan so that I can access capital.
\item US-2.2: As an approver, I want to approve or reject loans so that I can manage bank risk.
\item US-2.3: As a borrower, I want installment schedules for large loans so that repayment is manageable.
\item US-2.4: As a borrower, I want to chat with the bank so that I can discuss my loan application.
\end{itemize}

\textbf{Sprint 3 — AI/ML and Polish}
\begin{itemize}[noitemsep]
\item US-3.1: As a bank operator, I want fraud risk scores so that I can make informed approval decisions.
\item US-3.2: As a bank operator, I want explainable AI so that I understand why a loan is flagged.
\item US-3.3: As an admin, I want a risk dashboard so that I can monitor security across all loans.
\end{itemize}

\subsection{SDLC Stage Mapping}

The project maps to the seven stages of the Software Development Life Cycle (SDLC):

\begin{table}[H]
\centering
\caption{SDLC stage mapping.}
\small
\begin{tabular}{|p{2.8cm}|p{4.5cm}|p{4cm}|}
\hline
\textbf{SDLC Stage} & \textbf{Project Activity} & \textbf{Deliverable} \\
\hline
1. Planning \& Requirements & Feasibility studies; professor consultations; BCOLBD guideline review & Feasibility Report; Project Plan \\
\hline
2. Defining Requirements & System analysis (CSE471); use case definitions; constraints & CSE471 document; UC-1 through UC-5 \\
\hline
3. Designing Architecture & Three-layer architecture; DB schema (3NF); smart contract interfaces & Architecture diagrams; ERD; DFD \\
\hline
4. Development & Sprint 1--3: smart contracts, frontend, backend, AI/ML & Source code; DApp prototype \\
\hline
5. Testing & Hardhat unit tests (12+); integration testing; AI/ML evaluation & Test reports; model metrics \\
\hline
6. Deployment & Testnet deployment; frontend (Vercel); backend (Render) & Live prototype on testnet \\
\hline
7. Maintenance & Monitoring; model retraining; bug fixes; iteration & Updated docs; retrained models \\
\hline
\end{tabular}
\end{table}

\subsection{Design Decisions and Alternatives Considered}

For each major design decision, alternatives were evaluated and the first and second choices justified. The complete analysis is documented in the project decision justification report.

\begin{table}[H]
\centering
\caption{Summary of design decisions.}
\small
\begin{tabular}{|p{2.5cm}|p{2.8cm}|p{2.8cm}|p{3.2cm}|}
\hline
\textbf{Decision Area} & \textbf{1st Choice} & \textbf{2nd Choice} & \textbf{Key Criterion} \\
\hline
Methodology & Agile / Scrum & Incremental & Evolving scope, milestones \\
\hline
Architecture & DApp + Off-chain AI & Hybrid w/ Oracle & Gas cost, ML flexibility \\
\hline
Frontend & React + TypeScript & Vue + TypeScript & Web3 ecosystem \\
\hline
Smart Contract & EVM (Solidity) & Solana (Rust) & Ecosystem, free testnets \\
\hline
UI Design & MUI (Material 3) & Tailwind CSS & Banking UI, speed \\
\hline
Fraud Detection & Random Forest & XGBoost & SHAP, 94\%+ precision \\
\hline
Anomaly Detection & Isolation Forest & Autoencoder & Unsupervised, no labels \\
\hline
XAI Method & SHAP & LIME & Theory, regulatory \\
\hline
Database & PostgreSQL & SQLite & CSE370, 3NF, async \\
\hline
Hosting & Vercel + Render & Localhost & \$0 cost, public URL \\
\hline
\end{tabular}
\end{table}

%==============================================================================
\section{Feasibility Analysis}
%==============================================================================

\subsection{Technical Feasibility}

\begin{table}[H]
\centering
\caption{Technical feasibility.}
\small
\begin{tabular}{|p{2.5cm}|p{2.2cm}|p{6cm}|}
\hline
\textbf{Component} & \textbf{Assessment} & \textbf{Evidence} \\
\hline
Smart contracts & Fully feasible & Three contracts implemented, compiled, and tested with Hardhat (12+ passing unit tests); Solidity 0.8.20 with OpenZeppelin \\
\hline
Frontend DApp & Fully feasible & React 18 + TypeScript application with all pages implemented; Wagmi and RainbowKit provide mature wallet integration \\
\hline
Blockchain deployment & Fully feasible & Polygon Mumbai and Ethereum Sepolia testnets provide zero-cost, production-equivalent environments with free faucet access \\
\hline
AI/ML integration & Feasible with constraints & Random Forest inference on tabular data achieves sub-50ms latency; SHAP explanations computable in real-time; prototype scope limits to fraud detection \\
\hline
Database backend & Feasible & PostgreSQL schema designed (15 tables, 3NF); FastAPI provides async REST framework with automatic OpenAPI documentation \\
\hline
\end{tabular}
\end{table}

\textbf{Conclusion:} All core components are technically feasible within the prototype scope. The smart contract and frontend layers are already implemented and validated.

\subsection{Economic Feasibility}

\begin{table}[H]
\centering
\caption{Economic feasibility.}
\begin{tabular}{|l|p{3cm}|p{5.5cm}|}
\hline
\textbf{Cost Category} & \textbf{Estimate} & \textbf{Notes} \\
\hline
Blockchain deployment & \$0 & Public testnets (Sepolia, Mumbai) — no real cryptocurrency required \\
\hline
Frontend hosting & \$0 & Vercel free tier or localhost for demo \\
\hline
Backend hosting & \$0 & Render free tier or localhost \\
\hline
AI/ML training & \$0 & Local machine (16 GB RAM, 16 GB VRAM) or Google Colab free tier \\
\hline
Development tools & \$0 & Hardhat, VS Code, Git — all open-source \\
\hline
Total prototype cost & \textbf{\$0} & Entire prototype operates at zero financial cost \\
\hline
\end{tabular}
\end{table}

\textbf{Conclusion:} The prototype is economically viable at zero cost, leveraging free-tier services and open-source tooling.

\subsection{Operational and Schedule Feasibility}

\begin{table}[H]
\centering
\caption{Operational phases.}
\begin{tabular}{|l|p{8cm}|}
\hline
\textbf{Phase} & \textbf{Timeline / Activities} \\
\hline
Pre-Thesis 1 & Completed: Requirements analysis, system modeling, database design, software engineering planning, initial prototype \\
\hline
Pre-Thesis 2 & Current (8 weeks): Smart contract finalization, frontend completion, fraud detection implementation, documentation \\
\hline
Final Thesis & 4--8 weeks: Additional ML experiments, evaluation, final report, competition submission \\
\hline
\end{tabular}
\end{table}

The 8-week Agile plan distributes work across three sprints with defined deliverables per sprint. Risk mitigation includes: \textbf{Buffer:} Sprint 3 includes documentation and polish time as contingency. \textbf{Scope flexibility:} AI/ML features beyond fraud detection are designated as exploratory/future work. \textbf{Parallel workstreams:} Frontend, smart contract, and documentation tasks can proceed concurrently.

\subsection{Revenue Projection and Economic Impact}

The following projection models the annual revenue potential of the hierarchical lending system at full deployment scale. Calculations use a reference ETH price of \textbf{\$2,000} (February 2026 market rate) and interest rate parameters defined in Section IV.I.

\begin{table}[H]
\centering
\caption{Revenue projection assumptions.}
\small
\begin{tabular}{|p{5cm}|p{6.5cm}|}
\hline
\textbf{Parameter} & \textbf{Value} \\
\hline
Reference ETH price & \$2,000 (Feb 2026) \\
\hline
World Bank $\to$ National Bank rate & 3\% APR (wholesale inter-bank) \\
\hline
National Bank $\to$ Local Bank rate & 5\% APR (inter-bank) \\
\hline
Local Bank $\to$ Borrower rate & 8\% APR (retail lending, mid-range of 5--12\%) \\
\hline
Average loan term & 12 months \\
\hline
Loan turnover factor & 2$\times$ per year (6-month avg effective cycle) \\
\hline
Default rate provision & 3\% (conservative DeFi industry estimate) \\
\hline
Origination fee & 0.25\% per disbursement \\
\hline
\end{tabular}
\end{table}

\subsubsection{Tier 1 --- World Bank (Global Reserve)}

\begin{table}[H]
\centering
\caption{World Bank revenue projection (1,000,000 ETH reserve).}
\small
\begin{tabular}{|p{6cm}|r|r|}
\hline
\textbf{Metric} & \textbf{ETH} & \textbf{USD Equivalent} \\
\hline
Total reserve capital & 1,000,000 & \$2,000,000,000 \\
\hline
Disbursed to 5 National Banks & 1,000,000 & \$2,000,000,000 \\
\hline
Annual interest income (3\%) & 30,000 & \$60,000,000 \\
\hline
Origination fees (0.25\%) & 2,500 & \$5,000,000 \\
\hline
Less: Default provision (3\%) & $-$975 & $-$\$1,950,000 \\
\hline
\textbf{Net annual revenue} & \textbf{31,525} & \textbf{\$63,050,000} \\
\hline
\end{tabular}
\end{table}

\subsubsection{Tier 2 --- National Banks (5 Banks $\times$ 200,000 ETH)}

\begin{table}[H]
\centering
\caption{National Bank revenue projection (per bank and combined).}
\small
\begin{tabular}{|p{6cm}|r|r|}
\hline
\textbf{Metric (per National Bank)} & \textbf{ETH} & \textbf{USD Equivalent} \\
\hline
Capital received from World Bank & 200,000 & \$400,000,000 \\
\hline
Cost of capital (3\% to World Bank) & $-$6,000 & $-$\$12,000,000 \\
\hline
Disbursed to 10 Local Banks (10,000 each) & 100,000 & \$200,000,000 \\
\hline
Interest income from Local Banks (5\%) & 5,000 & \$10,000,000 \\
\hline
Retained reserve direct lending (100,000 ETH at 6\%) & 6,000 & \$12,000,000 \\
\hline
Origination fees (0.25\%) & 500 & \$1,000,000 \\
\hline
Less: Default provision (3\%) & $-$345 & $-$\$690,000 \\
\hline
\textbf{Net annual revenue per bank} & \textbf{5,155} & \textbf{\$10,310,000} \\
\hline
\textbf{Combined (5 banks)} & \textbf{25,775} & \textbf{\$51,550,000} \\
\hline
\end{tabular}
\end{table}

\subsubsection{Tier 3 --- Local Banks (50 Banks $\times$ 10,000 ETH)}

\begin{table}[H]
\centering
\caption{Local Bank revenue projection (per bank and combined).}
\small
\begin{tabular}{|p{6cm}|r|r|}
\hline
\textbf{Metric (per Local Bank)} & \textbf{ETH} & \textbf{USD Equivalent} \\
\hline
Capital received from National Bank & 10,000 & \$20,000,000 \\
\hline
Cost of capital (5\% to National Bank) & $-$500 & $-$\$1,000,000 \\
\hline
Loans issued: 20 borrowers $\times$ 1,000 ETH ($2\times$ turnover) & 20,000 & \$40,000,000 \\
\hline
Interest income from borrowers (8\%) & 1,600 & \$3,200,000 \\
\hline
Origination fees (0.25\% on 20,000 ETH) & 50 & \$100,000 \\
\hline
Less: Default provision (3\%) & $-$49.5 & $-$\$99,000 \\
\hline
\textbf{Net annual revenue per bank} & \textbf{1,100.5} & \textbf{\$2,201,000} \\
\hline
\textbf{Combined (50 banks)} & \textbf{55,025} & \textbf{\$110,050,000} \\
\hline
\end{tabular}
\end{table}

\subsubsection{Borrower Economics (1,000 Borrowers $\times$ 1,000 ETH)}

\begin{table}[H]
\centering
\caption{Borrower-level economics.}
\small
\begin{tabular}{|p{6cm}|r|r|}
\hline
\textbf{Metric (per Borrower)} & \textbf{ETH} & \textbf{USD Equivalent} \\
\hline
Average loan amount & 1,000 & \$2,000,000 \\
\hline
Annual interest cost (8\%) & 80 & \$160,000 \\
\hline
Estimated business return (15--20\% avg.) & 150--200 & \$300,000--400,000 \\
\hline
\textbf{Net borrower surplus (after interest)} & \textbf{70--120} & \textbf{\$140,000--240,000} \\
\hline
\textbf{Aggregate (1,000 borrowers)} & \textbf{70,000--120,000} & \textbf{\$140M--240M} \\
\hline
\end{tabular}
\end{table}

\subsubsection{System-Wide Revenue Summary}

\begin{table}[H]
\centering
\caption{System-wide annual revenue summary.}
\small
\begin{tabular}{|p{5.5cm}|r|r|}
\hline
\textbf{Tier} & \textbf{Annual Revenue (ETH)} & \textbf{USD Equivalent} \\
\hline
Tier 1: World Bank (1 entity) & 31,525 & \$63,050,000 \\
\hline
Tier 2: National Banks (5 entities) & 25,775 & \$51,550,000 \\
\hline
Tier 3: Local Banks (50 entities) & 55,025 & \$110,050,000 \\
\hline
\textbf{Total platform revenue} & \textbf{112,325} & \textbf{\$224,650,000} \\
\hline
Borrower surplus generated & 70,000--120,000 & \$140M--240M \\
\hline
\end{tabular}
\end{table}

\subsubsection{Global Economic Impact}

Beyond direct platform revenue, the Crypto World Bank creates broader economic value:

\begin{itemize}[noitemsep]
\item \textbf{Capital deployment:} \$2 billion in lending capital reaches 1,000 direct borrowers across developing economies. According to World Bank research on development finance, each dollar of institutional lending generates approximately \$2.5--3.0 in downstream economic activity through the fiscal multiplier effect, implying a potential \textbf{\$5--6 billion annual economic stimulus}.
\item \textbf{Job creation:} SME lending research (IFC, 2019) estimates that every \$50,000 in small business credit creates or sustains one job. At \$2 billion in deployed capital, the platform could support an estimated \textbf{40,000 direct jobs} in borrower enterprises.
\item \textbf{Financial inclusion:} Approximately 1.4 billion adults remain unbanked globally (World Bank Global Findex, 2021). The platform's retail-focused design provides transparent, accessible credit to underserved populations without requiring traditional banking relationships or credit histories.
\item \textbf{Transaction cost reduction:} DeFi lending eliminates intermediary costs associated with traditional cross-border development finance. Settlement occurs in minutes rather than days, and on Polygon PoS, transaction fees remain below \$0.01---representing a \textbf{60--80\% cost reduction} compared to traditional correspondent banking.
\item \textbf{Transparency dividend:} On-chain auditability reduces compliance and audit costs for participating institutions. Traditional bank audits cost \$500,000--\$2 million annually; blockchain-native audit trails significantly reduce this overhead.
\end{itemize}

\vspace{4pt}
\noindent\textit{\small\textbf{Sources for economic impact estimates:}
(a)~GDP multiplier (\$2.5--3.0$\times$): World Bank, ``World Development Report 2022: Finance for an Equitable Recovery,'' \url{https://www.worldbank.org/en/publication/wdr2022};
(b)~Job creation (\$50K per job): International Finance Corporation (IFC), ``MSME Finance Gap 2019,'' \url{https://www.ifc.org/en/insights-reports/2019/msme-finance-gap};
(c)~1.4 billion unbanked: World Bank, ``The Global Findex Database 2021,'' \url{https://www.worldbank.org/en/publication/globalfindex};
(d)~DeFi cost reduction (60--80\%): Bank for International Settlements, ``DeFi lending: intermediation without information?,'' BIS Working Paper No.~1183, 2024, \url{https://www.bis.org/publ/work1183.pdf};
(e)~Bank audit costs (\$500K--\$2M): Deloitte, ``Global Banking Outlook 2024.''}

%==============================================================================
\section{System Modeling}
%==============================================================================

\subsection{Use Case Diagram}

\textbf{Actors (4):} Borrower, Bank Approver, World Bank Admin, National Bank — \textbf{29 use cases total.} A high-level use case diagram is maintained in the project documentation repository.

\subsection{Sequence Diagram}

The loan request, AI risk assessment, and approval flow span \textbf{49 interaction steps} across 9 participants. Full sequence diagrams are maintained in the project documentation repository.

\subsection{Entity-Relationship Diagram}

The ERD comprises 15 entities in 3NF. Key relationships:
\begin{itemize}[noitemsep]
\item \texttt{WORLD\_BANK} (1) $\to$ (N) \texttt{NATIONAL\_BANK} $\to$ (N) \texttt{LOCAL\_BANK} — Hierarchical banking structure
\item \texttt{BORROWER} (1) $\to$ (N) \texttt{LOAN\_REQUEST}; \texttt{LOAN\_REQUEST} (1) $\to$ (N) \texttt{INSTALLMENT}, \texttt{CHAT\_MESSAGE}; \texttt{BORROWER} (1) $\to$ (1) \texttt{BORROWING\_LIMIT}
\item \texttt{LOAN\_REQUEST} / \texttt{TRANSACTION} $\to$ (N) \texttt{AI\_ML\_SECURITY\_LOG}
\end{itemize}

Full ERD is in the project documentation repository.

\subsection{Activity, Component, and Data Flow Diagrams}

Activity diagrams (loan request to repayment, income verification, chat system, AI chatbot, hierarchical banking, market data, profile management), component diagrams (presentation, smart contract, backend, external subsystems), and data flow diagrams (Level 0 context and Level 1 with 12 processes and 11 data stores) are documented in the project documentation repository.

%==============================================================================
\section{Valuation and Distribution Strategy}
%==============================================================================

\subsection{Value Proposition}

\begin{table}[H]
\centering
\caption{Value proposition.}
\small
\begin{tabular}{|p{3.2cm}|p{4.5cm}|p{3.5cm}|}
\hline
\textbf{Value Type} & \textbf{Description} & \textbf{Beneficiary} \\
\hline
Operational efficiency & Elimination of manual reconciliation and multi-day settlement & Banking institutions \\
\hline
Audit cost reduction & Real-time on-chain auditability replaces periodic third-party audits & Regulators, institutions \\
\hline
Risk mitigation & AI/ML-augmented loan decisioning reduces default rates & Lenders, borrowers \\
\hline
Financial inclusion & Transparent, programmable lending accessible to underserved populations & Borrowers in developing economies \\
\hline
Research contribution & Novel intersection of hierarchical DeFi, AI security, and governance & Academic community \\
\hline
\end{tabular}
\end{table}

\subsection{Revenue Model}

\begin{table}[H]
\centering
\caption{Revenue model.}
\begin{tabular}{|p{3.5cm}|p{5.5cm}|p{2cm}|}
\hline
\textbf{Revenue Stream} & \textbf{Mechanism} & \textbf{Phase} \\
\hline
Loan origination fees & Configurable percentage (0.1--0.5\%) deducted at disbursement via smart contract & Phase 2 \\
\hline
Premium analytics services & Subscription-based access to advanced AI risk dashboards for institutional users & Phase 3 \\
\hline
Governance token economics & Network participation incentives distributed via governance token & Phase 3 \\
\hline
Grant and pilot funding & Academic research grants; regulatory sandbox program funding & Phase 1--2 \\
\hline
\end{tabular}
\end{table}

\subsection{Go-to-Market Strategy}

\begin{table}[H]
\centering
\caption{Go-to-market phases.}
\begin{tabular}{|p{2.8cm}|p{6cm}|p{2.5cm}|}
\hline
\textbf{Phase} & \textbf{Activities} & \textbf{Timeline} \\
\hline
Phase 1: Academic Validation & Competition submission (BCOLBD 2025); thesis publication; open-source release & Current \\
\hline
Phase 2: Pilot Deployment & Regulatory sandbox application; partnership with one institutional entity; testnet-to-mainnet migration & 6--12 months \\
\hline
Phase 3: Production Scale & Multi-chain deployment; full AI/ML backend; commercial partnerships; governance token launch & 12--24 months \\
\hline
\end{tabular}
\end{table}

\subsection{Launch Readiness}

\begin{itemize}[noitemsep]
\item Whitepaper and technical documentation: \textbf{Published.}
\item Smart contract suite: \textbf{Implemented and tested} (WorldBankReserve, NationalBank, LocalBank).
\item Frontend DApp: \textbf{Implemented} (all pages, responsive, wallet integration).
\item Prototype deployment: \textbf{Ready} for testnet deployment.
\item AI/ML backend: \textbf{Architecture defined}; implementation in progress.
\end{itemize}

%==============================================================================
\section{Conclusion}
%==============================================================================

The Crypto World Bank addresses a \textbf{complex, multi-party coordination and trust problem} in hierarchical development finance by leveraging the unique properties of blockchain technology: immutability, programmable enforcement, and cryptographic auditability. The solution goes beyond existing DeFi lending protocols by introducing a four-tier institutional hierarchy, AI/ML-augmented risk assessment, and a comprehensive governance framework that addresses network membership, business operations, and technology infrastructure.

The platform is positioned at the intersection of decentralized finance, institutional lending, and applied AI security—a combination that is presently unaddressed in both the academic literature and the commercial blockchain landscape. With a working prototype, a defined market and partnership strategy, transparent risk assessment, and a phased go-to-market plan, the Crypto World Bank represents a viable and scalable contribution to the emerging field of blockchain-based development finance.

%==============================================================================
\appendix
%==============================================================================

\section{Technology Stack}

\begin{table}[H]
\centering
\begin{tabular}{|l|l|l|}
\hline
\textbf{Layer} & \textbf{Technology} & \textbf{Version / Notes} \\
\hline
Smart Contract & Solidity, OpenZeppelin & 0.8.20; Ownable, ReentrancyGuard \\
\hline
Frontend & React, TypeScript, Vite, Material-UI & React 18; MUI v5; Material Design 3 theme \\
\hline
Wallet Integration & Wagmi, RainbowKit, Viem & EIP-1193 compliant \\
\hline
Build and Test & Hardhat & Automated test suite; deployment scripts \\
\hline
Target Networks & Polygon Mumbai, Ethereum Sepolia & Public testnets; zero-cost operation \\
\hline
AI/ML (planned) & Python, FastAPI, scikit-learn, SHAP & Random Forest, Isolation Forest, SHAP \\
\hline
\end{tabular}
\end{table}

\section{Smart Contract Capabilities}

The platform's three smart contracts collectively support the following operations:

\begin{itemize}[noitemsep]
\item \textbf{World Bank Reserve Contract:} Reserve management, deposit handling, national bank registration, fund distribution to national banks, system pause/unpause, emergency withdrawal, and global statistics.
\item \textbf{National Bank Contract:} Local bank registration, borrowing from the world bank reserve, fund distribution to local banks, and network status queries.
\item \textbf{Local Bank Contract:} Loan requests, loan approval and rejection, installment payments, bank user management, and approver designation.
\end{itemize}

\section{References}

\begin{enumerate}[label={[\arabic*]}]
\item S.~M. Werner, D.~Perez, L.~Gudgeon, A.~Klages-Mundt, D.~Harz, and W.~J. Knottenbelt, ``SoK: Decentralized Finance (DeFi),'' \textit{arXiv preprint arXiv:2101.08778}, 2022. [Online]. Available: \url{https://arxiv.org/abs/2101.08778}
\item M.~Bartoletti and L.~Pompianu, ``An empirical analysis of smart contracts: platforms, applications, and design patterns,'' in \textit{Proc. Int. Conf. Financial Cryptography and Data Security}, pp.~494--509, 2017. DOI: \url{https://doi.org/10.1007/978-3-319-70278-0_31}
\item L.~Gudgeon, S.~Werner, D.~Perez, and W.~J. Knottenbelt, ``DeFi protocols for loanable funds: Interest rates, liquidity and market efficiency,'' in \textit{Proc. ACM Conf. Advances in Financial Technologies (AFT)}, 2020. DOI: \url{https://doi.org/10.1145/3419614.3423254}
\item P.~Tolmach, Y.~Li, S.~W. Lin, and Y.~Liu, ``A survey of smart contract formal specification and verification,'' \textit{ACM Computing Surveys}, vol.~54, no.~7, pp.~1--38, 2021. DOI: \url{https://doi.org/10.1145/3464421}
\item G.~Angeris and T.~Chitra, ``A note on privacy in constant function market makers,'' \textit{arXiv preprint arXiv:2103.01193}, 2022. [Online]. Available: \url{https://arxiv.org/abs/2103.01193}
\item R.~Auer and R.~Böhme, ``The technology of retail central bank digital currencies,'' \textit{BIS Quarterly Review}, pp.~85--100, Mar.~2020. [Online]. Available: \url{https://www.bis.org/publ/qtrpdf/r_qt2003j.htm}
\item D.~K.~C. Lee, L.~Yan, and Y.~Wang, ``A global perspective on central bank digital currency,'' \textit{China Economic Journal}, vol.~14, no.~1, pp.~52--66, 2021. DOI: \url{https://doi.org/10.1080/17538963.2020.1870279}
\item H.~Rahouti, K.~Xiong, and N.~Ghosh, ``Bitcoin concepts, threats, and machine-learning security solutions,'' \textit{IEEE Access}, vol.~6, pp.~67189--67205, 2018. DOI: \url{https://doi.org/10.1109/ACCESS.2018.2870243}
\item F.~Poursafaei, G.~B. Hamad, and Z.~Zilic, ``Detecting malicious Ethereum entities via application of machine learning classification,'' in \textit{Proc. IEEE Int. Conf. Blockchain Computing and Applications}, 2020. DOI: \url{https://doi.org/10.1109/BCCA50787.2020.9274081}
\item W.~Chen, Z.~Zheng, J.~Cui, E.~Ngai, P.~Zheng, and Y.~Zhou, ``Detecting Ponzi schemes on Ethereum: Towards healthier blockchain technology,'' in \textit{Proc. WWW Conference}, pp.~1409--1418, 2018. DOI: \url{https://doi.org/10.1145/3178876.3186046}
\item F.~T. Liu, K.~M. Ting, and Z.-H. Zhou, ``Isolation Forest,'' in \textit{Proc. IEEE Int. Conf. Data Mining (ICDM)}, pp.~413--422, 2008. DOI: \url{https://doi.org/10.1109/ICDM.2008.17}
\item M.~Ahmed, A.~N. Mahmood, and M.~R. Islam, ``A survey of anomaly detection techniques in financial domain,'' \textit{Future Generation Computer Systems}, vol.~55, pp.~278--288, 2016. DOI: \url{https://doi.org/10.1016/j.future.2015.01.001}
\item S.~M. Lundberg and S.-I. Lee, ``A unified approach to interpreting model predictions,'' in \textit{Advances in Neural Information Processing Systems (NeurIPS)}, pp.~4765--4774, 2017. [Online]. Available: \url{https://proceedings.neurips.cc/paper/2017/hash/8a20a8621978632d76c43dfd28b67767-Abstract.html}
\item P.~Bracke, A.~Datta, C.~Jung, and S.~Sen, ``Machine learning explainability in finance: An application to default risk analysis,'' \textit{Bank of England Staff Working Paper No.~816}, 2019. [Online]. Available: \url{https://www.bankofengland.co.uk/working-paper/2019/machine-learning-explainability-in-finance}
\item N.~Atzei, M.~Bartoletti, and T.~Cimoli, ``A survey of attacks on Ethereum smart contracts (SoK),'' in \textit{Proc. Int. Conf. Principles of Security and Trust (POST)}, pp.~164--186, 2017. DOI: \url{https://doi.org/10.1007/978-3-662-54455-6_8}
\item R.~Beck, C.~Müller-Bloch, and J.~L. King, ``Governance in the blockchain economy: A framework and research agenda,'' \textit{Journal of the Association for Information Systems}, vol.~19, no.~10, pp.~1020--1034, 2018. DOI: \url{https://doi.org/10.17705/1jais.00518}
\item P.~De Filippi and A.~Wright, \textit{Blockchain and the Law: The Rule of Code}. Harvard University Press, 2018. [Online]. Available: \url{https://www.hup.harvard.edu/books/9780674976429}
\item BCOLBD 2025, ``Blockchain Olympiad Bangladesh: Guideline and Evaluation Scheme,'' 2025. [Online]. Available: \url{https://bcolbd.org/uploads/guideline/BLOCKCHAIN\%20OLYMPIAD\%20BANGLADESH\%20Blockchain\%20Guideline.pdf}
\item OpenZeppelin, ``OpenZeppelin Contracts,'' 2024. [Online]. Available: \url{https://openzeppelin.com/contracts}
\end{enumerate}

\end{document}
